Design and Implementation of Probabilistic Programming Language Anglican

### 2017-02-22 paper/paper.tex
minor

In the implementation of Anglican, inference algorithms are
instantiations of the (ad-hoc) polymorphic function
\texttt{infer} declared as Clojure's multimethod\iftoggle{full}{
in the \texttt{anglican.{\linebreak[0]}inference}
namespace}{}. The function accepts an algorithm identifier,
a query --- the probabilistic program in which to perform the
inference, an initial value for the query, and optional
algorithm parameters.

@@

Let us illustrate this implementation step with
\textit{importance sampling},
the simplest inference algorithm.
Here is an implementation of the \texttt{infer} function for the algorithm:
\begin{lstlisting}[style=default]
(derive ::algorithm
        :anglican.inference/algorithm)
;; invoked when algo parameter is :importance
(defmethod infer :importance 
  [algo prog value & {}]
  (letfn
    ;; recursive function without any parameter
    [sample-seq 
      []
      ;; lazy infinite sequence 
      (lazy-seq
        (cons
          (:state (exec ::algorithm prog value
                        initial-state))
          (sample-seq))))]
    (sample-seq)))
\end{lstlisting}
This implementation is dispatched 
when \texttt{infer} receives \texttt{:importance} as its \texttt{algo} 
parameter. (Anglican includes multiple implementations of \texttt{infer}
for different inference algorithms.) Once dispatched, it lazily 
constructs an infinite sequence of inference states by repeatedly 
executing the program \texttt{prog} using \texttt{exec}
and retrieving the final inference state of the execution 
using \texttt{:state}. For checkpoint handlers, importance sampling simply
relies on their default implementations.
%\texttt{anglican.importance/{\linebreak[0]}infer} just calls
%\texttt{anglican.inference/{\linebreak[0]}exec} and relies on default
%implementations of checkpoint handlers.

>>>>

In the implementation of Anglican, inference algorithms are
instantiations of the (ad-hoc) polymorphic function
\texttt{infer} declared as Clojure's multimethod\iftoggle{full}{
in the \texttt{anglican.{\linebreak[0]}inference}
namespace}{}. The function accepts an algorithm identifier,
a query (the probabilistic program in which to perform the
inference), an initial value for the query, and optional
algorithm parameters.

@@

Let us illustrate this implementation step with
\textit{importance sampling},
the simplest inference algorithm.
Here is an implementation of the \texttt{infer} function for the algorithm:
\begin{lstlisting}[style=default]
;; Make ::algorithm be converted to 
;; :anglican.inference/algorithm whenever necessary
(derive ::algorithm :anglican.inference/algorithm)

;; invoked when algo parameter is :importance
(defmethod infer :importance 
  [algo prog value & {}]
  (letfn
    ;; recursive function without any parameter
    [sample-seq 
      []
      ;; lazy infinite sequence 
      (lazy-seq
        (cons
          (:state (exec ::algorithm prog value
                        initial-state))
          (sample-seq))))]
    (sample-seq)))
\end{lstlisting}
This implementation is dispatched 
when \texttt{infer} receives \texttt{:importance} as its \texttt{algo} 
parameter. (Anglican includes multiple implementations of \texttt{infer}
for different inference algorithms.) Once dispatched, it lazily 
constructs an infinite sequence of inference states by repeatedly 
executing the program \texttt{prog} using \texttt{exec}
and retrieving the final inference state of the execution 
using \texttt{:state}. For checkpoint handlers, importance sampling simply
relies on their default implementations.
%\texttt{anglican.importance/{\linebreak[0]}infer} just calls
%\texttt{anglican.inference/{\linebreak[0]}exec} and relies on default
%implementations of checkpoint handlers.
